% Insurance Terminology
%
% Intended to be included within its own section.

\begindeptgroup{it}

\begin{description}
  \dt{calculation}
  Any computation performed for the purpose of returning to the caller.

  \dt{Calc DSL}
  The domain-specific language written to handle classifications and
  calculations; compiles into JavaScript.

  \dt{caller}
  User or system that performed a rating request.

  \dt{classification}
  A set of criteria---to be run by a classifier---that returns a boolean value
  of true if a given datum meets the criteria; otherwise, false. The return
  value shall have the same dimensions as the input datum.

  \dt{classifier}
  A system that performs any number of classifications.

  \dt{fail}
  Within context of an operation: The implementation \shallnot return the
  results of any calculation.

  \dt{number}
  A scalar of type integer or float

  \dt{matrix}
  A two-dimensional array of numbers; a vector of vectors.

  \dt{Program Client}
  The graphical user interface available on the LoVullo website used to gather
  data from the user for purposes of providing a quote or indication;
  communicates with Quote Server.

  \dt{Quote Server}
  Software that serves requests from the Program Client, performing activities
  such as serving steps, saving data entered by the user, and proxying rate
  requests.

  \dt{program}
  A line of business.

  \dt{rater}
  Software that produces a set of premiums that are the result of applying
  well-defined calculations to classified input data.

  \dt{vector}
  A one-dimensional array of numbers.
\end{description}

\enddeptgroup
