% Authorization Parties

\begindeptgroup{pm}

\index{authorization|(}
\label{s:authorize}

\sigauth{NL}
This specification is currently a draft and requires that each requirement be
verified and authorized for development.

\sigauth{NL}
An authorization indicates that a member of the indicated party or parties with
sufficient knowledge on topic affirms that the requirement is---to the best of
his or her knowledge---accurate and suitable for incorporation into an
implementation of the specification.

\sigauth{NL}
\p{signcomp} A signature line next to content that is not a numbered paragraph
is a \dfn{significant component}.

\sigauth{NL}
\begin{ex}
  \signline
  This example is not a paragraph but still contains a signature line; it is
  therefore a significant component under the definition of \pref{signcomp}.
\end{ex}

\sigauth{NL}
Each paragraph and significant component of the specification, unless incomplete
or previously authorized, contains a line that may be used for the initials of a
member of the party indicated in parenthesis. If multiple parties are
applicable, they will be separated with slashes.

\sigauth{NL}
Only a member of the party knowledgeable on the topic \shall provide their
authorization.

\sigauth{NL}
An authorization is performed by (a)~signing one's initials on the provided line
or (b)~indicating the paragraph number (or, for significant components, an
appropriate notation containing at least the section number and a unique
identifier for the significant component itself) via some \unspecified\ method
of correspondence that explicitly indicates each and every individual
authorization.

\sigauth{NL}
A particular authorization is valid until the authorized paragraph or significant
component is modified from its authorized form.

\sigauth{NL}
Signature lines with no authorization party listed \shallnot be authorized until
at least one party has been chosen.

\goodbreak
\begin{description}
  \sigauth{NL}
  \dt{C}
  Compliance department.

  \sigauth{NL}
  \dt{IT}
  A programmer from the IT~department.

  \sigauth{NL}
  \dt{PM}
  A project manager; defined as an individual who is responsible for making
  decisions regarding the direction and scope of the project.

  \sigauth{NL}
  \dt{UW}
  An underwriter, assistant underwriter or someone with equivalent underwriting
  knowledge.
\end{description}

\index{authorization|)}

\enddeptgroup
